ext_risk_copula

### 2019-01-22 ext_risk_copula.Rmd
error fixed in qbinom function

ricker_extrisk_d0<-readRDS("./Results/ricker/ricker_extrisk_d0.RDS")
numsims<-10000
ricker_extrisk_d0$CI0.025left<-qbinom(ricker_extrisk_d0$risk_left_d0,size=numsims,prob=0.025)/numsims
ricker_extrisk_d0$CI0.975left<-qbinom(ricker_extrisk_d0$risk_left_d0,size=numsims,prob=0.975)/numsims

ricker_extrisk_d0$CI0.025right<-qbinom(ricker_extrisk_d0$risk_right_d0,size=numsims,prob=0.025)/numsims
ricker_extrisk_d0$CI0.975right<-qbinom(ricker_extrisk_d0$risk_right_d0,size=numsims,prob=0.975)/numsims

@@

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(0,2),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,angle=90,length=0.05,col=rgb(1,0,0,0.5),code=3)

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025right,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975right,angle=90,length=0.05,col=rgb(0,0,1,0.5),code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

@@

hassell_extrisk_d0$CI0.025left<-qbinom(hassell_extrisk_d0$risk_left_d0,size=numsims,prob=0.025)/numsims
hassell_extrisk_d0$CI0.975left<-qbinom(hassell_extrisk_d0$risk_left_d0,size=numsims,prob=0.975)/numsims

hassell_extrisk_d0$CI0.025right<-qbinom(hassell_extrisk_d0$risk_right_d0,size=numsims,prob=0.025)/numsims
hassell_extrisk_d0$CI0.975right<-qbinom(hassell_extrisk_d0$risk_right_d0,size=numsims,prob=0.975)/numsims

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.4,7.6),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.05,col=rgb(1,0,0,0.5),code=3)

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025right,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975right,angle=90,length=0.05,col=rgb(0,0,1,0.5),code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

@@

msmith_extrisk_d0$CI0.025left<-qbinom(msmith_extrisk_d0$risk_left_d0,size=numsims,prob=0.025)/numsims
msmith_extrisk_d0$CI0.975left<-qbinom(msmith_extrisk_d0$risk_left_d0,size=numsims,prob=0.975)/numsims

msmith_extrisk_d0$CI0.025right<-qbinom(msmith_extrisk_d0$risk_right_d0,size=numsims,prob=0.025)/numsims
msmith_extrisk_d0$CI0.975right<-qbinom(msmith_extrisk_d0$risk_right_d0,size=numsims,prob=0.975)/numsims

pdf("./Results/msmith/msmith_extrisk_d0.pdf",height = 6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.05,col=rgb(1,0,0,0.5),code=3)

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.05,col=rgb(0,0,1,0.5),code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model with no dispersion : rc=1.33); numlocs=5, numsteps=25, numsims=10000\label{fig_msmith_risk_d0}](./Results/msmith/msmith_extrisk_d0.pdf){ width=40%, height=40% }

@@

@@

>>>>

ricker_extrisk_d0<-readRDS("./Results/ricker/ricker_extrisk_d0.RDS")
numsims<-10000
ricker_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_left_d0)/numsims
ricker_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_left_d0)/numsims

ricker_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_right_d0)/numsims
ricker_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_right_d0)/numsims

@@

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(0,2),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025right,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

@@

hassell_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=hassell_extrisk_d0$risk_left_d0)/numsims
hassell_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=hassell_extrisk_d0$risk_left_d0)/numsims

hassell_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=hassell_extrisk_d0$risk_right_d0)/numsims
hassell_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=hassell_extrisk_d0$risk_right_d0)/numsims

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.4,7.6),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025right,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

@@

msmith_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims
msmith_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims

msmith_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=msmith_extrisk_d0$risk_right_d0)/numsims
msmith_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=msmith_extrisk_d0$risk_right_d0)/numsims

pdf("./Results/msmith/msmith_extrisk_d0.pdf",height = 6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0.8,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model with no dispersion : rc=4/3); numlocs=5, numsteps=25, numsims=10000\label{fig_msmith_risk_d0}](./Results/msmith/msmith_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r fig_pennycuick_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
pennycuick_extrisk_d0<-readRDS("./Results/pennycuick/pennycuick_extrisk_d0.RDS")

pennycuick_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=pennycuick_extrisk_d0$risk_left_d0)/numsims
pennycuick_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=pennycuick_extrisk_d0$risk_left_d0)/numsims

pennycuick_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=pennycuick_extrisk_d0$risk_right_d0)/numsims
pennycuick_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=pennycuick_extrisk_d0$risk_right_d0)/numsims

pdf("./Results/pennycuick/pennycuick_extrisk_d0.pdf",height = 6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = c(2,7),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025right,x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(3,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model with no dispersion : rc=4.3231657); numlocs=5, numsteps=25, numsims=10000\label{fig_pennycuick_risk_d0}](./Results/pennycuick/pennycuick_extrisk_d0.pdf){ width=40%, height=40% }
